Capstone Movielens Report

### 2025-10-23 reports/capstone-movielens.site/05.appendix.Rmd
Fix for the functions' descriptions.

Builds a string from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1).

@@

::: { #func.get_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.get_log1.args.arg1 .sidebar }
  - **arg1:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.get_log1.args.msg_template) argument.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.get_log1.args.msg_template) and [arg1](#func.get_log1.args.arg1)  arguments, respectively.

@@

Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:
  - [arg.name](#func.msg.set_arg.args.arg.name): name of the element; 
  - [arg](#func.msg.set_arg.args.arg): the element value.

@@

::: { #func.msg.set_arg.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.msg.set_arg.args.arg.name .sidebar }
  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument. 
:::

::: { #func.msg.set_arg.args.arg .sidebar }
  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.set_arg.args.msg_template) argument.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.set_arg.args.msg_template) and [arg](#func.msg.set_arg.args.arg)  arguments, respectively.

@@

Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:
  - [arg.name](#func.msg.glue.args.arg.name): name of the element; 
  - [arg](#func.msg.glue.args.arg): the element value.

@@

::: { #func.msg.glue.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.msg.glue.args.arg.name .sidebar }
  - **arg.name:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument. 
:::

::: { #func.msg.glue.args.arg .sidebar }
  - **arg:** The value to replace the format elements represented by the substring `%1` in the message template specified by the [msg_template](#func.msg.glue.args.msg_template) argument.

>>>>

Builds a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1) argument.

@@

::: { #func.get_log1.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of the pattern `%1` to be replaced by the value specified by the [arg1](#func.get_log1.args.arg1) argument.

@@

::: { #func.get_log1.args.arg1 .sidebar }
  - **arg1:** Value to replace all occurrences of the pattern `%1` in the message template passed in the [msg_template](#func.get_log1.args.msg_template) argument.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a character vector from the template passed in the [msg_template](#func.get_log1.args.msg_template) argument using the format value specified by the [arg1](#func.get_log1.args.arg1)  argument.

@@

Builds a message string from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg] argument;

  - [arg](#func.msg.set_arg.args.arg): the value to replace all occurrences of the pattern passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument.

@@

::: { #func.msg.set_arg.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument.

@@

::: { #func.msg.set_arg.args.arg.name .sidebar }
  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.

::: { #func.msg.set_arg.args.arg .sidebar }
  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument. 
:::
:::

@@

This function internally calls [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format value specified by the [arg](#func.msg.set_arg.args.arg)  argument to replace all occurances of the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument (`%1` by default).

@@

Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.glue.args.arg.name): name of the element;

  - [arg](#func.msg.glue.args.arg): the element value.

@@

::: { #func.msg.glue.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring specified by the [arg.name](#func.msg.msg.glue.args.arg.name) argument.

@@

::: { #func.msg.glue.args.arg.name .sidebar }
  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.msg.glue.args.arg) argument.
:::

::: { #func.msg.glue.args.arg .sidebar }
  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.
